---
title: "Data preparation"
output:
  pdf_document: default
---

# Instructions

- You only need to submit the .Rmd of this file, not a PDF.

- You should __comment__ your code clearly to show what you've done to prepare the data.

- The purpose of this file is to use the data in the `data-raw` folder to create the data you will use in the report. The data you will use in the report should be saved in the `data` folder. It is good professional practice to make sure you're never directly modifying your raw data, but instead creating new datasets based on merges/manipulations that you need to reuse.

- Make sure you've taken a look at the hints for the web scraping and census API. 

- You may find the `write_rds()` function from the `readr` package helpful (it is loaded as part of the `tidyverse`).

- You do not need to keep the structure below.

# Set up

```{r, libraries}
library(cancensus)
```

# Loading client data

```{r}
cust_dev <- readRDS("data-raw/cust_dev.Rds")
cust_sleep <- readRDS("data-raw/cust_sleep.Rds")
customer <- readRDS("data-raw/customer.Rds")
device <- readRDS("data-raw/device.Rds")
```

# Getting external data

## Web scraping industry data

```{r}
url <- "https://fitnesstrackerinfohub.netlify.app"

target <- bow(url,
              user_agent = "sherryxiaoman.lu@mail.utoronto.ca for STA303/1002 final project",
              force = TRUE)
target

html <- scrape(target)

device_data <- html %>% 
  html_elements("table") %>% 
  html_table() %>% 
  pluck(1)

save(device_data, file = "data-raw/device_data.RData")
```

# Census API

```{r}
## Simplify to only needed variables
options(cancensus.api_key = "CensusMapper_c35605992b233a54f504b09dcd8d5687",
        cancensus.cache_path = "cache")

regions <- list_census_regions(dataset = "CA16")

regions_filtered <-  regions %>% 
  filter(level == "CSD") %>% # CSD are Census Subdivision; it is a geographic level
  as_census_region_list()

census_data_csd <- get_census(dataset='CA16', regions = regions_filtered,
                          vectors=c("v_CA16_2397"),
                          level='CSD', geo_format = "sf")

median_income <- census_data_csd %>% 
  as_tibble() %>% 
  select(CSDuid = GeoUID, contains("median"), Population) %>% 
  mutate(CSDuid = parse_number(CSDuid)) %>% 
  rename(hhld_median_inc = 2)

save(median_income, file = "data-raw/median_income.RData")
```
